---
title: "MultiLogit_MaxEntropyClassif"
output: html_document
date: "2023-01-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Multinomial Logit analysys or Maximun Entropy Classifier


## 1) First way: Multinomial logit analysis by  proportional hazard regression model 

```{r}
library(survival)
choco_candy<-read.csv("C:\\Users\\Leobardo\\Documents\\GitHub\\MultiLogit_MaxEntropyClassif\\choco_candy.csv")
```


Coef: Multinomial Logit Parameter Estimates

se(coef): Estandard Error

Chi-Square: z^2

Pr > ChiSq: Pr(>|z|)



```{r}
output1<-coxph(Surv(Subj,Choice)~Dark+Soft+Nuts, data=choco_candy,
               ties="breslow")
summary(output1)
```

## Probability of choice

To get the probabilities of each alternative




```{r}
predict(output1)
```

Alternatives and predicted value (exponential)

```{r}
exp_p<- cbind(choco_candy$Alt, data.frame(exp(predict(output1))))[1:8,]
exp_p
```

Rename variables


```{r}
names(exp_p)[1]<-"Alt"
names(exp_p)[2]<-"Exp"
```


Calculating probability of choice:

$$p(c_i|C)=\frac{exp(x_i\beta)}{\sum _{j=1}^mexp(x_j\beta)}$$

```{r}
exp_p$prob<-exp_p$Exp/sum(exp_p$Exp)
exp_p$prob
```

change the order of the probability of choice:

Choice of chocolate candies

```{r}
exp_p[c(order(-exp_p$prob)),]
```




## 2) Second way: Multinomial logit analysis by mlogit

```{r}
library(mlogit)
```

Understanding data structure

```{r}
head(choco_candy)
```

convert choco_candy data to a mlogit data format

```{r}
TM<-mlogit.data(choco_candy,choice="Choice", shape="long",
                chid.var="Subj", alt.var="Alt", drop.index=TRUE)

TM
```


We need to add 0 because we do not have an intercept, if not, there is an error.

```{r}
output2<-mlogit(Choice ~ 0 + Dark+Soft+Nuts, data=TM)
summary(output2)
```


## Probability of choice

To get the probabilities of each alternative




```{r}
predict(output2)
```

Alternatives and predicted value (exponential)

```{r}
exp_p<- cbind(choco_candy$Alt, data.frame(exp(predict(output2))))[1:8,]
exp_p
```

Rename variables


```{r}
names(exp_p)[1]<-"Alt"
names(exp_p)[2]<-"Exp"
```


Calculating probability of choice:

$$p(c_i|C)=\frac{exp(x_i\beta)}{\sum _{j=1}^mexp(x_j\beta)}$$

```{r}
exp_p$prob<-exp_p$Exp/sum(exp_p$Exp)
exp_p$prob
```

change the order of the probability of choice:

Choice of chocolate candies

```{r}
exp_p[c(order(-exp_p$prob)),]
```



## 3) Third way. Rchoice library

```{r}
library(Rchoice)
```

```{r}
output3<-Rchoice(Choice ~ 0 + Dark + Soft + Nuts, data = TM, 
                 family =binomial("logit") )
summary(output3)
```
## Coefficients




```{r}
coef<-output3$coefficients
coef
```

```{r}
coef_percent<-(exp(coef)-1)*100
coef_percent
```






